Attestable Expiration with Trusted Platform Modules

### 2016-05-17 paper.tex
More on the protocol

The problem with the straw man is that it requires extending the same trust to Charlie that we do to Bob. Charlie can retain $K$ as long as he likes and distribute it as widely as he wishes---e.g., to Mallory---and moreover he can repudiate doing so without any way for Alice to prove otherwise.

@@

@@

\item Alice sends a Flicker PAL (Piece of Application Logic) to Charlie. Alice asks Charlie to run it with the input parameter "-bootstrap".

\item When Charlie runs the PAL, the PAL establishes a secure channel as per section 4.4.2 of the Flicker paper. That is, it generates a public/private key pair, outputs the public key, and puts the private key in sealed storage.

\item Charlie sends Alice a Flicker attestation of the execution and output. After verifying the attestation, Alice knows that a) her PAL was executed, and b) it produced the attested public key.

\item Alice encrypts K with the secure channel public key sends it to Charlie. Charlie stores the ciphertext of the key. Alice then goes offline, but not before completing step 7 below.

\item In order to request K, Bob sends his public key to Charlie. Charlie runs the PAL with three inputs: the "-divulge" flag, the ciphertext of K, and Bob's public key. The PAL decrypts K using the secure channel private key, re-encrypts it using Bob's public key, and produces the re-encrypted key as output. Charlie sends the output to Bob.

\item If Charlie runs the PAL with the parameter "-destroy", the PAL will sign the statement "Key destroyed" with the secure channel private key. It will then destroy the secure channel private key. The output is the signed statement.

\item Before going offline, Alice wrote an Ethereum contract that said, "If Charlie provides a statement that reads 'Key destroyed' when decrypted with this secure channel public key, I will pay him X ether."

@@

@@

>>>>

The problem with the straw man is that it requires extending the same trust to Charlie that we do to Bob. Charlie can retain $K$ as long as he likes and distribute it as widely as he wishes---e.g., to Mallory---and moreover he can repudiate his misbehavior without any way for Alice to prove otherwise.

@@

Alice and Charlie can perform a protocol as follows:

@@

\item Alice sends a Flicker PAL to Charlie. The PAL has an input parameter called `mode' which can take one of the following values: `initialize', `divulge', or `destroy'.

\item Alice asks Charlie to run the PAL with the input `mode=initialize'. When Charlie runs the PAL, the PAL establishes a secure channel. That is, it generates a public/private key pair, outputs the public key, and stores the private key in the TPM such that only this PAL is able to read it.

\item Charlie sends Alice the PAL's output as well as a Flicker attestation of the execution. After verifying the attestation, Alice knows that a) her PAL was executed, and b) it produced the attested public key.

\item Alice encrypts $K$ with the secure channel public key and sends it to Charlie. Charlie stores the ciphertext of $K$. Alice then goes offline, but not before writing an Ethereum contract, described below as step 8.

\item In order to request $K$, Bob sends his public key to Charlie. Charlie runs the PAL with three inputs: `mode=divulge', the ciphertext of $K$, and Bob's public key. The PAL decrypts $K$ using the secure channel private key, re-encrypts it using Bob's public key, and produces the re-encrypted key as output. Charlie sends the output to Bob.

\item When the PAL is run using `mode=divulge', it also produces as output an append-only log that contains one entry for every public key to whom Charlie has divulged $K$. The log is signed using the secure channel private key. This log must be included on subsequent executions that use `mode=divulge' so that the PAL can add another entry if necessary. The PAL can confirm that the required log has been provided and protect against replay attacks by using a monotonic counter, described in Flicker 4.3.2.

\item If Charlie runs the PAL with inputs comprising `mode=destroy' and the divulgence log, the PAL will append to the log the statement ``key destroyed''. It will then destroy the secure channel private key.

\item Before going offline, Alice wrote an Ethereum contract that said, ``If Charlie publishes before time $t$ a log that can be decrypted using this public key and whose last entry is ``key destroyed", I will pay him $X$ ether."

@@

If Charlie produces proof that he destroyed the key, he earns his commission and Alice knows that $K$ can never be divulged again. If he never claims his commission, then Alice knows that something is wrong. Although she can not prove

@@

Note that the protocol as written does not restrict to whom Charlie divulges the key. However, it produces a non-repudiable record of the persons to whom it has been divulged.
